Exploring how changes in cause of death have narrowed the black-white life expectancy gap in the United States.

### 2017-02-23 Manuscript/Manuscript_COD_decomp.Rmd
new results

*To re-write*: To calculate 95% credible intervals, we sampled 1000 times from the posterior distribution to create 1000 samples for each stratum. We performed all calculations on each sample and took the median of the estimates as the estimate and the 2.5 and 97.5th quantiles as the lower and upper bound for the 95% CI. Anything about thinning?

All data analyses were performed using R version 3.3.1. The Bayesian smoothing was performed using `JAGS` (version X.X), and the life expectancy and decomposition analysis were performed using user-written functions found in the Supplement.

>>>>

*ktm to read over*: The bayesian model was fit using two markov chains of length 10,000. One thousand iterations remained after discarding the first two thousand iterations as burn-in and sampling every eighth iteration (to reduce autocorrelation). These 1,000 iterations approximate the shape of the posterior distribution, and we used the mean as the estimate of the log mortality rate, and the 2.5th and 97.5th percentiles as the lower and upper bound of the 95% credible interval (CI).

All data analyses were performed using R version 3.3.1. The Bayesian smoothing was performed using `rjags` (version 4-6) and `R2jags` (version 0.5-7), and the life expectancy and decomposition analysis were performed using user-written functions found in the Supplement.
